Bayesian Rate Estimation

### 2012-08-16 many.tex

\subsubsection{Loudest event statistic}
If we were to include only the $k$-loudest events in the posterior
distribution, rather than all observed events, the posterior
(Eq.~\eqref{eq:posterior}) would be modified by an additional factor
of $\exp[R_f \hat{F}(x_{N-k+1}, \theta) + R_b
  \hat{B}(x_{N-k+1},\theta)]$, where we have assumed events are
ordered by loudness, so that $x_{N-k+1}$ is the $k$-th loudest
event. This term accounts for the data-dependent threshold that a
loudest event statistic employs.

For the usual $k=1$ case \citep{Biswas2009}, the marginalised
posterior (Eq.~\eqref{eq:rate-shape-posterior}) becomes
\begin{equation}
p_{\rm LE}\left( R_f, R_b, \theta | d \right) \propto \left(R_f
\hat{f}(x_N,\theta) + R_b \hat{b}(x_N,\theta)\right)\exp\left[-\left(
  R_f (1-\hat{F}(x_N,\theta)) + R_b (1-\hat{B}(x_N,\theta)) \right)
  \right] \frac{p(\theta)}{\sqrt{R_f R_b}}.
\end{equation}
where $x_N$ denotes the loudness of the loudest event. Marginalising
over $R_b$ we obtain
\begin{equation}
p_{\rm LE}\left( R_f, \theta | d \right) \propto \left(
\frac{\hat{b}(x_N,\theta)}{2(1-\hat{B}(x_N,\theta))} + R_f
\hat{f}(x_N,\theta)\right)\frac{\sqrt{\pi}}{\sqrt{1-\hat{B}(x_N,\theta)}\,\sqrt{R_f}}
\exp(-R_f(1-\hat{F}(x_N,\theta))) .
\end{equation}
This posterior has a maximum in $R_f$ at
\begin{equation}
R_f =
\frac{\hat{f}(x_N,\theta)-(1-\hat{F}(x_N,\theta)\tilde{b}(x_N,\theta)
  \pm
  \sqrt{(\hat{f}(x_N,\theta)-(1-\hat{F}(x_N,\theta)\tilde{b}(x_N,\theta))^2
    -
    4\tilde{b}(x_N,\theta)(1-\hat{F}(x_N,\theta))\hat{f}(x_N,\theta)}}{4
  \hat{f}(x_N,\theta)(1-\hat{F}(x_N,\theta)}.
\end{equation}
where $\tilde{b}(x_N,\theta)
=\hat{b}(x_N,\theta)/(1-\hat{B}(x_N,\theta))$. If
$\tilde{b}(x_N,\theta) \ll 1$, i.e., the loudest event is very likely
to be foreground, we obtain the result $(1- \hat{F}(x_N,\theta))\,R_f
\approx 1/2$. This is can be understood as the statement that the rate
of foreground events with ranking statistic greater than $x_N$, $(1-
\hat{F}(x_N,\theta))\,R_f$, is of order $1$, as expected. If
$\tilde{b}(x_N,\theta) >> 1$, however, the posterior on $R_f$ is
peaked at $0$.

\subsubsection{Foreground dominated statistic}
If we set the threshold for including an event, $x_{\rm min}$,
sufficiently high, we can ensure that $\hat{f}(x_i,\theta) \gg
\hat{b}(x_i,\theta)$ for all ranking statistics $x_i$ in the data
set. The posterior can then be approximated by
\begin{equation}
p_{\rm FD}\left( R_f, R_b, \theta | d \right) \propto \prod_{i} \left[
  \hat{f}\left(x_i, \theta\right)\right] R_f^N \exp\left[-\left( R_f +
  R_b \right) \right] \frac{p(\theta)}{\sqrt{R_f R_b}}.
\end{equation}
Normalisation over $R_b$ gives a constant factor and the posterior on
the foreground rate becomes
\begin{equation}
p_{\rm FD}\left( R_f, \theta | d \right) \propto \prod_{i} \left[
  \hat{f}\left(x_i, \theta\right)\right] R_f^{N-\frac{1}{2}}
\exp\left[-R_f \right] p(\theta).
\end{equation}
Ignoring the dependence on $\theta$, this is peaked at a rate $R_f =
N-1/2$, so we have the expected result that, in the foreground
dominated regime, the rate is approximately equal to the number of
events observed. We note that this is the rate of events occurring
above threshold and so if we were to use this statistic with different
choices of threshold we would have to renormalise the rates to a fixed
threshold in order to compare the results.

@@

Suppose we attempt to detect gravitational wave signals in a data
stream by matched filtering in the frequency domain against a set of
$N$ template waveforms \citep[e.g.,][]{findchirppaper,LVC2011}.  In
our simplistic model, we suppose the data stream consists of
stationary Gaussian noise with a power spectral density $S(f)$
combined additively with some number of gravitational wave signals.
We assume that the signals are sufficiently rare that they do not
overlap in the data stream.  The signal to noise ratio (SNR) of a
template, $h(f)$, given data, $d(f)$, is
\begin{equation}
  \rho_h \equiv \frac{\left\langle h, d \right\rangle}{\sqrt{\left
      \langle h, h \right\rangle}},
\end{equation}
where $\left \langle \cdot \right\rangle$ denotes the noise-weighted
inner product:
\begin{equation}
  \left\langle a, b \right\rangle \equiv \ilya{4 \Re} \int_0^\infty
  df\, \frac{a^*(f) b(f)}{S(f)}.
\end{equation}
We suppose for simplicity that the templates are sufficiently distinct
that
\begin{equation}
  \left\langle h_i, h_j \right\rangle \simeq \delta_{ij}.
\end{equation}
In the following subsection, we will generalize the model to
overlapping templates.  We rank candidate events by their maxmim SNR
over the entire template bank,
\begin{equation}
  x \equiv \max_{h} \rho_h,
\end{equation}
and consider only events that have a maximum SNR above some threshold,
$x > \xmin$.

For a data stream of pure noise, $d(f) = n(f)$, the SNR of a each
template follows a $N(0,1)$ distribution.  The background ranking
statistic (i.e.\ the maximum SNR over the template bank) then has a
cumulative distribution without thresholding of
\begin{equation}
  \hat{B}(x) = \left( \frac{1 + \erf\left( \frac{x}{\sqrt{2}}
    \right)}{2} \right)^N
\end{equation}
Imposing the threshold, $x > \xmin$, the cumulative distribution of
the background becomes
\begin{equation}
  \label{eq:analytic-background-rate}
  \hat{B}(x) = \frac{\left( 1 + \erf\left( \frac{x}{\sqrt{2}}
    \right) \right)^N - \left( 1 + \erf\left(
    \frac{\xmin}{\sqrt{2}} \right) \right)^N}{2^N - \left( 1 +
    \erf\left( \frac{\xmin}{\sqrt{2}} \right) \right)^N }
\end{equation}
\ilya{for $x>\xmin$, $0$ otherwise.}

@@

\ilya{Now, one interesting question that Fig.~3 brings to mind is the
  following: if we only used "gold-plated" events (say, those with
  $p(x|fore)/p(x|back)>0.99$, how much worse / more uncertain would
  the rate estimation be?]}

@@

In \S~\ref{sec:analytic-GW-example} we assumed that the overlap
between different templates in the template bank was negligible, so
the SNRs recovered by different templates are independent random
variables.  In fact, template banks are not constructed in this way
\citep[e.g.,][]{Owen:1998dk,Ajith:2008}, because signals could fall in
the gaps between the non-overlapping templates.  We can model this
effect by assuming that a template bank of $N$ actual templates will
behave as if it had $N_\mathrm{eff}$ \emph{independent} templates.
Rather than pre-computing $N_\mathrm{eff}$, we can fit for it as a
shape parameter.  That is, we assume that $\theta =
\{N_\mathrm{eff}\}$ is a shape parameter for the background cumulative
distribution:
\begin{equation}
  \hat{B}\left(x, N_\mathrm{eff}\right) = \frac{\left( 1 + \erf\left(
    \frac{x}{\sqrt{2}} \right) \right)^{N_\mathrm{eff}} - \left( 1 +
    \erf\left( \frac{\xmin}{\sqrt{2}} \right)
    \right)^{N_\mathrm{eff}}}{2^{N_\mathrm{eff}} - \left( 1 +
    \erf\left( \frac{\xmin}{\sqrt{2}} \right) \right)^{N_\mathrm{eff}} }.
\end{equation}

Results from such an analysis on the data in
\S~\ref{sec:analytic-GW-example} appear in Figures \ref{fig:rates-nt}
and \ref{fig:ntemplates}.  Recall that the parameters used to generate
this data set are $R_f = 10.4$, $R_b = 95.1$, and $N_\mathrm{eff} =
1000$.  We use a flat prior on $N_\mathrm{eff}$.  Both the rates and
the number of effective templates are recovered without significant
loss of accuracy relative to the fixed $N_\mathrm{eff}$ situation in
\S~\ref{sec:analytic-GW-example}.

\ilya{[Again, I think we need to explicitly compare this method with
    two alternatives.  Alternative one is the loudest event statistic.
    Alternative two is just counting gold-plated events, and dividing
    the volume in which we are sensitive to them by their number.  In
    principle, alternative one should be suboptimal when the number of
    events is more than 0 or 1, while alternative two should be OK
    when the number of events is large, but error-prone otherwise.
    But if we want people to use this technique, we have to defend the
    point that there is a regime where it is clearly superior (and say
    what that regime is).]}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{sky_location}
  \caption{\label{fig:sky-loc} Contours of the posterior probability
    distribution for the center of the cluster, $\vec{x}_0$, in the
    example from \S~\ref{sec:star-cluster}.  The center $(x,y) =
    \left(x_0, y_0\right)$ is determined to within a few percent of
    the structural radius of the cluster, $r_0$ (see
    Eq.~\eqref{eq:true-cluster-parameters}). \ilya{[Given the cluster
        size of 0.1, it seems a bit surprising that the center is off
        by $\sim 0.05$...]}}
\end{figure}

>>>>

\subsubsection{Loudest event statistic}
If we were to include only the $k$-loudest events in the posterior
distribution, rather than all observed events, the posterior
(Eq.~\eqref{eq:posterior}) would be modified by an additional factor
of $\exp[R_f \hat{F}(x_{N-k+1},\theta) + R_b
  \hat{B}(x_{N-k+1},\theta)]$, where we have assumed events are
ordered by loudness, so that $x_{N-k+1}$ is the $k$-th loudest
event. This term accounts for the data-dependent threshold that a
loudest event statistic employs.

For the usual $k=1$ case \citep{Biswas2009}, the marginalised
posterior (Eq.~\eqref{eq:rate-shape-posterior}) becomes
\begin{equation}
p_{\rm LE}\left( R_f, R_b, \theta | d \right) \propto \left(R_f
\hat{f}(x_N,\theta) + R_b \hat{b}(x_N,\theta)\right)\exp\left[-\left(
  R_f (1-\hat{F}(x_N,\theta)) + R_b (1-\hat{B}(x_N,\theta)) \right)
  \right] \frac{p(\theta)}{\sqrt{R_f R_b}}.
\end{equation}
where $x_N$ denotes the loudness of the loudest event. Marginalising
over $R_b$ we obtain
\begin{equation}
p_{\rm LE}\left( R_f, \theta | d \right) \propto \left(
\frac{\hat{b}(x_N,\theta)}{2(1-\hat{B}(x_N,\theta))} + R_f
\hat{f}(x_N,\theta)\right)\frac{\sqrt{\pi}\,
  p(\theta)}{\sqrt{1-\hat{B}(x_N,\theta)}\,\sqrt{R_f}}
\exp\left(-R_f(1-\hat{F}(x_N,\theta))\right) .
\end{equation}
This posterior has a maximum in $R_f$ at
\begin{equation}
R_f =
\frac{\hat{f}(x_N,\theta)-(1-\hat{F}(x_N,\theta)\tilde{b}(x_N,\theta)
  \pm
  \sqrt{(\hat{f}(x_N,\theta)-(1-\hat{F}(x_N,\theta)\tilde{b}(x_N,\theta))^2
    -
    4\tilde{b}(x_N,\theta)(1-\hat{F}(x_N,\theta))\hat{f}(x_N,\theta)}}{4
  \hat{f}(x_N,\theta)(1-\hat{F}(x_N,\theta)}.
\end{equation}
where $\tilde{b}(x_N,\theta)
=\hat{b}(x_N,\theta)/(1-\hat{B}(x_N,\theta))$. If
$\tilde{b}(x_N,\theta) \ll 1$, we obtain the result $(1-
\hat{F}(x_N,\theta))\,R_f \approx 1/2$. This is can be understood as
the statement that the rate of foreground events with ranking
statistic greater than $x_N$, $(1- \hat{F}(x_N,\theta))\,R_f$, is of
order $1$, as expected. However, $\tilde{b}(x_N,\theta) = -{\rm d}
[\ln(1-\hat{B}(x,\theta))]/{\rm d}x$ and $(1-\hat{B}(x,\theta))
\rightarrow 0$ as $x \rightarrow \infty$, so this term will be
divergent and for many reasonable examples, we will find
$\tilde{b}(x_N,\theta) >> \hat{f}(x_N,\theta)$, in which case the
posterior on $R_f$ is peaked at $0$. This issue highlights the problem
with using a loudest-event statistic with an improper prior on the
background rate $R_b$. No matter how improbable an event with $x=x_N$
is under the background distribution, it can become likely that the
event at $x_N$ is from the background distribution by taking the
background rate to be sufficiently large. Although this predicts many
more events with $x < x_N$, by using only the loudest event we do not
incorporate the information that no such events are seen. This problem
is avoided in the new framework described here, since we use all
events detected above threshold and combined rates, $R_f+R_b$,
significantly greater than the total number of observed events are
strongly disfavoured.

This problem can be avoided in the loudest event framework, by
including an upper limit on the rate, $R_{\rm max}$, in the prior for
$R_b$. The marginalised distribution for the foreground rate then
becomes
\begin{eqnarray}
p_{\rm LE}\left( R_f, \theta | d \right) &\propto& \left(
\frac{\hat{b}(x_N,\theta)}{(1-\hat{B}(x_N,\theta))^{\frac{3}{2}}}
\left[\frac{\sqrt{\pi}}{2}{\rm
    erf}\left(\sqrt{(1-\hat{B}(x_N,\theta))\,R_{\rm max}}\right) -
  \sqrt{(1-\hat{B}(x_N,\theta))\,R_{\rm max}} \, {\rm
    e}^{-(1-\hat{B}(x_N,\theta)) \, R_{\rm max}}\right]
\right. \nonumber \\ && \left.+ R_f
\hat{f}(x_N,\theta)\frac{\sqrt{\pi}\,{\rm
    erf}\left(\sqrt{(1-\hat{B}(x_N,\theta))\,R_{\rm
      max}}\right)}{\sqrt{(1-\hat{B}(x_N,\theta))}}\right)\frac{p(\theta)}{\sqrt{R_f}}
\exp\left(-R_f(1-\hat{F}(x_N,\theta))\right) \label{LEwithRmax},
\end{eqnarray}
where ${\rm erf}(x)$ is the error function, defined in the usual way
${\rm erf}(x) = (2/\sqrt{\pi}) \int_0^x \exp(-u^2){\rm d}u$. If
$(1-\hat{B}(x_N,\theta)) \, R_{\rm max} \ll 1$, Eq.~(\ref{LEwithRmax})
can be approximated by
\begin{equation}
p_{\rm LE}\left( R_f, \theta | d \right) \propto \left( \frac{R_{\rm
    max}}{3} \hat{b}(x_N,\theta) + R_f
\hat{f}(x_N,\theta)\right)\frac{p(\theta)}{\sqrt{R_f}}
\exp\left(-R_f(1-\hat{F}(x_N,\theta))\right)
\end{equation}
and if $\hat{f}(x_N,\theta) \gg R_{\rm max} \hat{b}(x_N.\theta)$ we
find the same result as before $(1- \hat{F}(x_N,\theta))\,R_f \approx
1/2$.

\subsubsection{Foreground dominated statistic}
If we set the threshold for including an event, $x_{\rm min}$,
sufficiently high, we can ensure that $\hat{f}(x_i,\theta) \gg
\hat{b}(x_i,\theta)$ for all ranking statistics $x_i$ in the data
set. The posterior can then be approximated by
\begin{equation}
p_{\rm FD}\left( R_f, R_b, \theta | d \right) \propto \prod_{i} \left[
  \hat{f}\left(x_i, \theta\right)\right] R_f^N \exp\left[-\left( R_f +
  R_b \right) \right] \frac{p(\theta)}{\sqrt{R_f R_b}}.
\end{equation}
Normalisation over $R_b$ gives a constant factor and the posterior on
the foreground rate becomes
\begin{equation}
p_{\rm FD}\left( R_f, \theta | d \right) \propto \prod_{i} \left[
  \hat{f}\left(x_i, \theta\right)\right] R_f^{N-\frac{1}{2}}
\exp\left[-R_f \right] p(\theta).
\end{equation}
Ignoring the dependence on $\theta$, this is peaked at a rate $R_f =
N-1/2$, so we have the expected result that, in the foreground
dominated regime, the rate is approximately equal to the number of
events observed. We note that the rate $R_f$ is defined as the rate of
events occurring above the specified threshold and therefore if the
foreground dominated statistic were used to estimated rates $R_f^1$
and $R_f^2$ for thresholds $x_{\rm min}=x_1$, $x_{\rm min}=x_2$
respectively, these rates should be compared by equating $R_f^1
(1-\hat{F}(x_2,\theta))$ and $R_f^2 (1-\hat{F}(x_1,\theta))$.

@@

Suppose we attempt to detect gravitational wave signals in a data
stream by matched filtering in the frequency domain against a set of
$N$ template waveforms \citep[e.g.,][]{findchirppaper,LVC2011}.  In
our simplistic model, we suppose the data stream consists of
stationary Gaussian noise with a power spectral density $S(f)$
combined additively with some number of gravitational wave signals.
We assume that the signals are sufficiently rare that they do not
overlap in the data stream.  The signal to noise ratio (SNR) of a
template, $h(f)$, given data, $d(f)$, is
\begin{equation}
  \rho_h \equiv \frac{\left\langle h, d \right\rangle}{\sqrt{\left
      \langle h, h \right\rangle}},
\end{equation}
where $\left \langle \cdot \right\rangle$ denotes the noise-weighted
inner product:
\begin{equation}
  \left\langle a, b \right\rangle \equiv 4 \Re \int_0^\infty df\,
  \frac{a^*(f) b(f)}{S(f)}.
\end{equation}
We suppose for simplicity that the templates are sufficiently distinct
that
\begin{equation}
  \left\langle h_i, h_j \right\rangle \simeq \delta_{ij}.
\end{equation}
In the following subsection, we will generalize the model to
overlapping templates.  We rank candidate events by their maxmim SNR
over the entire template bank,
\begin{equation}
  x \equiv \max_{h} \rho_h,
\end{equation}
and consider only events that have a maximum SNR above some threshold,
$x > \xmin$.

For a data stream of pure noise, $d(f) = n(f)$, the SNR of a each
template follows a $N(0,1)$ distribution.  The background ranking
statistic (i.e.\ the maximum SNR over the template bank) then has a
cumulative distribution without thresholding of
\begin{equation}
  \hat{B}(x) = \left( \frac{1 + \erf\left( \frac{x}{\sqrt{2}}
      \right)}{2} \right)^N
\end{equation}
where ${\rm erf}(x)$ is the error function as before. Imposing the
threshold, $x > \xmin$, the cumulative distribution of the background
becomes
\begin{equation}
  \label{eq:analytic-background-rate}
  \hat{B}(x) = \frac{\left( 1 + \erf\left( \frac{x}{{\sqrt{2}}} \right)
    \right)^N - \left( 1 + \erf\left( \frac{\xmin}{{\sqrt{2}}} \right)
    \right)^N}{2^N - \left( 1 + \erf\left( \frac{\xmin}{{\sqrt{2}}} \right)
    \right)^N }
\end{equation}
for $x>\xmin$, $0$ otherwise.

@@

We can compare these results to results obtained using the two
approximations described earlier, the loudest-event statistic and the
foreground-dominated statistic. The marginalised distribution for the
foreground rate using these alternatives are shown in
Figure~\ref{fig:altmeth}. In this case, the loudest event had
$x_N=9.5$\jon{(correct this)}. The loudest-event statistic depends on
a specification of the maximum, $R_{\rm max}$, for the background
rate. We show results for $R_{\rm max}=\infty$, i.e.m, the improper
prior, and $R_{\rm max}=10000$. The results for other reasonable
choices of $R_{\rm max} = 100, 1000, 100000$ etc. gave exactly the
same posterior, since $\hat{b}(x_N,) R_{\rm max} \ll \hat{f}(x_N)$ for
all these choices and we are therefore in the regime where the
posterior is insensitive to $R_{\rm max}$. To apply the
foreground-dominated statistic we must specify a threshold above which
we assume all events are foreground. It is reasonable to do this based
on a specification for the relative probability of an event being
fore/background, $\hat{f}(x)/\hat{b}(x)=p_{\rm thresh}$. Setting
$p_{\rm thresh}=0.99$ gives $x_{\rm min}=4.07$ and there are $N=13$
events exceeding that threshold. Setting $p_{\rm thresh}=0.5$ gives
$x_{\rm min}=3.82$ and there are $N=15$ events exceeding that
threshold \jon{(correct these numbers using Will's data)}. We show
results for both of these choices of $x_{\rm min}$ in
Figure~\ref{fig:altmeth}. We also show similar results for two extreme
cases --- setting $x_{\rm min}=3.5$ so that we assume all $98$
observed events are foreground; and setting $x_{\rm min}=9$ so that
only the loudest event is classified as foreground.

The loudest event statistic with the improper-prior gives, as
expected, a poor approximation to the foreground rate. The peak is
more accurately located when a prior maximum rate is defined, but the
distribution is much wider than using the full analysis described
here. This is to be expected as much of the information is being
thrown away. The foreground-dominated statistic gives a reasonable
approximation to the true foreground rate, and a distribution that is
not much wider than the full analysis, for the non-extreme choices of
$x_{\rm min}$. For $x_{\rm min}=9$, the foreground dominated statistic
has equivalent performance to the loudest event statistic, as we might
expect, while when $x_{\rm min}=3.5$, it performs poorly since we are
approximating the foreground rate by the total foreground plus
background rate. This indicates that, provided the threshold is chosen
appropriately, the foreground dominated statistic can perform quite
well at estimating the rate. The fact that it reproduces the posterior
from the full analysis so well is indicative of the fact that most of
the information about the foreground comes from the loudest
events. Indeed, for $x_{\rm min} \approx 4$, the set of events
consists mostly of foreground sources and that set contains a decent
number of events ($13$), so it is not surprising that this statistic
can estimate the foreground rate well. The choice of $x_{\rm min}$ was
motivated by knowledge of $\hat{b}(x,\theta)$ and $\hat{f}(x,\theta)$,
which we have in this case, but this might not be possible if the
parameters $\theta$ were simultaneously being estimated. The full
analysis naturally incorporates inference about the rate parameters
$\theta$ and the background rate $R_b$ along with the foreground rate
and incorporates maximum information from the data set and should
therefore lead to narrower posteriors in general.

@@

In \S \ref{sec:analytic-GW-example} we assumed that the overlap
between different templates in the template bank was negligible, so
the SNRs recovered by different templates are independent random
variables.  In fact, template banks are not constructed in this way
\citep[e.g.,][]{Owen:1998dk,Ajith:2008},
%\citep{Caudill2011,Cannon2011}, 
because signals could fall in the gaps between the non-overlapping
templates.  We can model this effect by assuming that a template bank
of $N$ actual templates will behave as if it had $N_\mathrm{eff}$
\emph{independent} templates.  Rather than pre-computing
$N_\mathrm{eff}$, we can fit for it as a shape parameter.  That is, we
assume that $\theta = \{N_\mathrm{eff}\}$ is a shape parameter for the
background cumulative distribution:
\begin{equation}
  \hat{B}\left(x, N_\mathrm{eff}\right) = \frac{\left( 1 + \erf\left( \frac{x}{\sqrt{2}} \right)
    \right)^{N_\mathrm{eff}} - \left( 1 + \erf\left( \frac{\xmin}{\sqrt{2}} \right)
    \right)^{N_\mathrm{eff}}}{2^{N_\mathrm{eff}} - \left( 1 + \erf\left( \frac{\xmin}{\sqrt{2}} \right)
    \right)^{N_\mathrm{eff}} }.
\end{equation}

Results from such an analysis appear in Figures \ref{fig:rates-nt} and
\ref{fig:ntemplates}.  We use the same parameters and data set as in
\S \ref{sec:analytic-GW-example}, with $R_f = 10.4$, $R_b = 95.1$, and
$N_\mathrm{eff} = 1000$, but now allow $N_\mathrm{eff}$ to be a
parameter of the background distribution, with a flat prior.  Both the
rates and the number of effective templates are recovered without
significant loss of accuracy relative to the fixed $N_\mathrm{eff}$
situation in \S \ref{sec:analytic-GW-example}.

If we consider the two alternative methods, the loudest event and
foreground dominated statistics, we will recover the same foreground
distributions as in the case with $N_{\rm eff}$ fixed, which are shown
in Figure~\ref{fig:altmeth}. This is because the parameter $N_{\rm
  eff}$ affects only the background distribution, to which the
foreground-dominated statistic is insensitive, and in the loudest
event case, after marginalisation over $N_{\rm eff}$ we find
$\int_0^{N_{\rm max}} \hat{b}(x_N,N_{\rm eff}) {\rm d}N_{\rm eff} \ll
3 N_{\rm max}/R_{\rm max} \hat{f}(x_N, N_{\rm eff})$ and so we are
still in the foreground-dominated regime in which the loudest event
tells us nothing about the background. Similarly, neither of these
alternative methods can inform us about the value of $N_{\rm eff}$, a
property of the background. \jon{Technically, if we allowed really
  large values of $N_{\rm eff}$ we would get into a regime where the
  loudest event could be background and we'd get something here. But,
  we would need $N_{\rm max} \sim 10^{20}$ and so I don't think we
  should consider these alternatives further in this case.}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{sky_location}
  \caption{\label{fig:sky-loc} Contours of the posterior probability
    distribution for the center of the cluster, $\vec{x}_0$, in the
    example from \S~\ref{sec:star-cluster}.  The center $(x,y) =
    \left(x_0, y_0\right)$ is determined to within about 5\%
    of the structural radius of the cluster, $r_0$ (see
    Eq.~\eqref{eq:true-cluster-parameters}). \ilya{[Given the cluster
        size of 0.1, it seems a bit surprising that the center is off
        by $\sim 0.05$...]} \will{That is $0.1*r_0$, not $0.1$!}}
\end{figure}
